Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-05 paper/content/barriers.tex
more tweaks

The first is that competition dynamics can lead to small asymmetries in data between firms amplifying into large effects through the same mechanism as the death spiral effect discussed in the previous section.

The second is that data can serve as a larger barrier to entry when exploration is reputationally costly. This is due to the fact that the incumbent can explore actions in the incumbency period without immediate reputational consequences, whereas in order for the entrant to acquire the same data it needs to incur the immediate reputational consequences. As a result, when the incumbent does exploration in the incumbency period the value of the data accumulated is higher and it is harder for an entrant to compete.
}

>>>>

The first is that small asymmetries in data between firms can amplify into large effects through the same mechanism as the death spiral effect discussed in the previous section.

The second is that data can serve as a larger barrier to entry when exploration is reputationally costly. This is due to the fact that the incumbent can explore actions in the incumbency period without immediate reputational consequences, whereas in order for the entrant to acquire the same data it needs to incur the immediate reputational consequences. As a result, when the incumbent does exploration in the incumbency period the value of the data accumulated is higher and it is harder for an entrant to compete in the market.
}
